---
title: "Victorian Electricity Retail: Offer Characteristics & Customer Transfers"
author: "Arzu Khanna"
date: "2025-12-05"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    theme: cosmo
    df_print: paged
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(
echo = FALSE,
message = FALSE,
warning = FALSE,
results = "asis"
)
```

```{r libraries}

library(dplyr)
library(lubridate)
library(ggplot2)
library(plotly)
library(readxl)
library(tidyr)
library(zoo)
library(here)
library(bit64)
library(corrplot)
library(randomForest)
library(xgboost)
library(car)
library(knitr)
library(kableExtra)

options(digits = 4)
```


## Data Loading & Preparation

This section loads the electricity offer dataset, transfer datasets, and prepares cleaned inputs for further analysis.

```{r load-offers}
# 1.1 Load electricity offer data

# 1. Get VEC electricity data
offer_data_raw <- read_excel("VEC Elec Offers with CPRG VDO.xlsx") %>%
  mutate(Fuel = "electricity")

# 2. Keep only data from 2022 onwards and only market offers
# Offers before 2022 were recorded quarterly instead of monthly so may cause
# inconsistencies - therefore are excluded.

offer_data <- offer_data_raw %>%
  filter(year(identifier_date) >= 2022,
         offer_type == "market offer")

# 3. Keep only the most recent identifier_date for each offer_id
offer_data <- offer_data %>%
  group_by(offer_id) %>%
  filter(identifier_date == max(identifier_date)) %>%
  ungroup()

# 3. Convert date columns to proper date format
offer_data <- offer_data %>%
  mutate(
    identifier_date = ymd(identifier_date),  # Format: YYYY-MM-DD
    start_date = ymd(start_date)
  )

# 4. Calculate end_date as last day of month for identifier_date
# If identifier_date is the maximum date in the dataset, leave end_date blank (NA)
# as the offer may still be available in the following month

max_identifier_date <- max(offer_data$identifier_date, na.rm = TRUE)

offer_data <- offer_data %>%
  mutate(
    end_date = case_when(
      identifier_date == max_identifier_date ~ as.Date(NA),
      TRUE ~ ceiling_date(identifier_date, "month") - days(1)
    )
  )

# 5. Create offer categories
offer_data <- offer_data %>%
  mutate(
    offer_category = case_when(
      has_discount == 1 & has_disc_conditional == 1 ~ "Conditional discounts",
      has_discount == 1 & has_disc_conditional == 0 ~ "Guaranteed discounts",
      has_discount == 0 & has_disc_conditional == 0 ~ "No discounts",
      TRUE ~ "Other"
    )
  )
```

```{r}
cat("### Offer Dataset Summary\n")

summary_table <- tibble(
  Metric = c(
    "Total offers loaded", "Retailers represented", "Range of identifier dates", 
    "Latest identifier date"),
  Value = c(
    scales::comma(nrow(offer_data)),
    offer_data %>% pull(retailer) %>% n_distinct(), 
    paste0(min(offer_data$identifier_date, na.rm=TRUE), 
           " → ", max(offer_data$identifier_date, na.rm=TRUE)),
          as.character(max_identifier_date)
    )
  )

kable(summary_table, "html") %>%
kable_styling(full_width = FALSE, position = "left")
```

```{r load-transfers}
# 1.2 Load transfer data
transfers_raw <- readRDS(here("02_data", "transfers_raw.rds"))

# Transfers OUT
transfers_out_daily <- transfers_raw %>%
  filter(
    stat_shortcut == "M57A", 
    Year >= 2022, 
    crcode %in% 1000:1040) %>%
  mutate(
    stat_date = ymd(stat_date)) %>%
  rename(
    transfer_date = stat_date, 
    transfers_count = stat_value,
    from_retailer = FRMP_Retailer_name, 
    to_retailer = NEWFRMP_Retailer_name)

# Transfers IN
transfers_in_daily <- transfers_out_daily %>%
  rename(retailer = to_retailer)

# Customer base
customer_base <- transfers_raw %>%
  filter(
    stat_shortcut == "M71", 
    year(ymd(stat_date)) >= 2022) %>%
  group_by(
    Year = Year, Month = Month, retailer = FRMP_Retailer_name) %>%
  summarise(
    customer_count = sum(as.numeric(stat_value)), .groups = "drop")

message("✓ Transfers loaded")
```

```{r}
cat("### Transfer Dataset Summary\n")

transfer_summary <- tibble(
  Metric = c(
    "Total transfer rows (daily)", "Transfers IN rows", "Transfers OUT rows", 
    "Retailers represented (M57A)", "Date range"),
  Value = c(
    scales::comma(nrow(transfers_raw)),
    scales::comma(nrow(transfers_in_daily)),
    scales::comma(nrow(transfers_out_daily)),
    transfers_out_daily$from_retailer %>% n_distinct(),
    paste0(min(transfers_out_daily$transfer_date, na.rm=TRUE),
           " → ", max(transfers_out_daily$transfer_date, na.rm=TRUE))
    )
  )

kable(transfer_summary, "html") %>%
kable_styling(full_width = FALSE, position = "left")
```

## Offer Snapshots, Weekly Aggregation & Lag Features

This section constructs weekly offer snapshots, aggregates transfer data to weekly frequency, and creates lagged feature sets for modelling.

```{r create-snapshots}

# 2.1 Weekly Offer Snapshot: Function to calculate offer metrics

calculate_offer_metrics <- function(offers, target_date, retailer_name) {
  
  # Retailer’s active offers at this date
  active <- offers %>%
    filter(retailer == retailer_name, start_date <= target_date,
           (is.na(end_date) | end_date >= target_date))
  
  # If no active offers
  if (nrow(active) == 0) 
    {return(tibble(date = target_date, retailer = retailer_name, n_offers = 0))}
  
  # Victorian-wide median bill at this point in time
  vic_median <- offers %>%
    filter(start_date <= target_date, (is.na(end_date) | end_date >= target_date)) %>%
    summarise(m = median(total_bill_pre_transaction, na.rm = TRUE)) %>% pull(m)
  
  # Summarise retailer metrics
  active %>%
    summarise(
      date = target_date, retailer = retailer_name, n_offers = n(),
      median_price = median(total_bill_pre_transaction, na.rm = TRUE),
      min_price = min(total_bill_pre_transaction, na.rm = TRUE),
      max_price = max(total_bill_pre_transaction, na.rm = TRUE),
      pct_guaranteed = mean(offer_category == "Guaranteed discounts") * 100,
      pct_conditional = mean(offer_category == "Conditional discounts") * 100,
      pct_no_discount = mean(offer_category == "No discounts") * 100,
      pct_solar = mean(solar_offer %in% c("Yes", "Optional")) * 100,
      pct_incentive = mean(has_incentive == "Yes") * 100,
      avg_annual_fee = mean(total_annual_fee, na.rm = TRUE),
      avg_late_fee = mean(total_late_payment_fee, na.rm = TRUE),
      vic_median = vic_median,
      price_vs_market = ((median_price - vic_median) / vic_median) * 100,
      cprg_retailer_size = first(cprg_retailer_size)
    )
}
```

```{r}
# 2.2 Generate Weekly Dates + Retailer Snapshots
weekly_dates <- seq.Date(as.Date("2022-01-03"), Sys.Date(), by = "week")

retailers <- unique(offer_data$retailer)

# Expand grid of all retailer × dates
offer_snapshots <- expand.grid(date = weekly_dates, retailer = retailers, stringsAsFactors = FALSE) %>%
  rowwise() %>%
  do(calculate_offer_metrics(offer_data, .$date, .$retailer)) %>%
  ungroup() %>%
  group_by(date) %>%
  mutate(price_rank = rank(median_price, ties.method = "average")) %>%
  ungroup()

message("✓ Snapshots created")
```

```{r}
cat("### Snapshot Summary\n")

snap_tbl <- tibble(
Metric = c("Total weekly snapshot rows", "Distinct retailers", "Date coverage"),
Value = c(scales::comma(nrow(offer_snapshots)), n_distinct(offer_snapshots$retailer), paste0(min(offer_snapshots$date), " → ", max(offer_snapshots$date))))

kable(snap_tbl, "html") %>%
kable_styling(full_width = FALSE, position = "left")
```

```{r aggregate-weekly}
# 2.3 Weekly Aggregation of Transfers
# Convert daily transfers (IN/OUT) to weekly totals and join with customer base for normalisation.

transfers_out_weekly <- transfers_out_daily %>%
  mutate(week = floor_date(transfer_date, "week", week_start = 1)) %>%
  group_by(week, Year, Month, retailer = from_retailer) %>%
  summarise(total_out = sum(transfers_count), .groups = "drop") %>%
  left_join(customer_base, by = c("Year", "Month", "retailer")) %>%
  mutate(
    total_out = as.numeric(total_out),
    rate_out = (total_out / customer_count) * 100
  ) %>%
  rename(date = week)

transfers_in_weekly <- transfers_in_daily %>%
  mutate(week = floor_date(transfer_date, "week", week_start = 1)) %>%
  group_by(week, Year, Month, retailer) %>%
  summarise(total_in = sum(transfers_count), .groups = "drop") %>%
  left_join(customer_base, by = c("Year", "Month", "retailer")) %>%
  mutate(
    total_in = as.numeric(total_in),
    rate_in = (total_in / customer_count) * 100
  ) %>%
  rename(date = week)
```

```{r}
cat("### Weekly Transfer Summary\n")

weekly_summary <- tibble(
Metric = c("Weekly OUT rows", "Weekly IN rows", "Retailers represented", "Date range"),
Value = c(scales::comma(nrow(transfers_out_weekly)), 
          scales::comma(nrow(transfers_in_weekly)),
          n_distinct(transfers_out_weekly$retailer),
          paste0(min(transfers_out_weekly$date), " → ", max(transfers_out_weekly$date))))

kable(weekly_summary, "html") %>%
kable_styling(full_width = FALSE, position = "left")
```

```{r}
# 2.4 Create Net Transfers (IN – OUT)

transfers_net <- transfers_in_weekly %>%
  distinct(date, retailer, .keep_all = TRUE) %>%
  left_join(
    transfers_out_weekly %>% 
      distinct(date, retailer, .keep_all = TRUE) %>%
      select(date, retailer, total_out, rate_out),
    by = c("date", "retailer"),
    relationship = "one-to-one"
  ) %>%
  mutate(
    net_transfers = total_in - coalesce(total_out, 0),
    net_rate = rate_in - coalesce(rate_out, 0)
  )

message("✓ Weekly aggregation complete")
```

```{r create-lags}
# 2.5 Create lagged datasets (1w, 2w, 4w, 8w)

create_lag <- function(offers, transfers, lag_w) {
  offers %>%
    mutate(date = date + weeks(lag_w)) %>%
    rename_with(~paste0(., "_lag", lag_w, "w"), -c(date, retailer)) %>%
    right_join(transfers, by = c("date", "retailer"))
}

message("Creating lagged datasets...")
```

```{r}
# 2.6 Build Lagged Version of OUT Dataset
data_out <- transfers_out_weekly %>%
  left_join(offer_snapshots, by = c("date", "retailer"))

for (lag in c(1, 2, 4, 8)) {
  lag_data <- create_lag(offer_snapshots, transfers_out_weekly, lag) %>% 
    select(date, retailer, ends_with(paste0("_lag", lag, "w")))
  data_out <- data_out %>% left_join(lag_data, by = c("date", "retailer"))
}

# Filter for retailers with sufficient data (100+ weeks of offers)
data_out <- data_out %>%
  group_by(retailer) %>% filter(n() >= 100) %>% ungroup() %>%
  filter(!is.na(customer_count))
```

```{r}
# 2.7 Build Lagged Version of IN Dataset

# IN analysis with multiple lags
data_in <- transfers_in_weekly %>%
  left_join(offer_snapshots, by = c("date", "retailer"))

for (lag in c(1, 2, 4, 8)) {
  lag_data <- create_lag(offer_snapshots, transfers_in_weekly, lag) %>% 
    select(date, retailer, ends_with(paste0("_lag", lag, "w")))
  data_in <- data_in %>% left_join(lag_data, by = c("date", "retailer"))
}

data_in <- data_in %>%
  group_by(retailer) %>% filter(n() >= 100) %>% ungroup() %>%
  filter(!is.na(customer_count))
```

## Exploratory Data Analysis

This section summarises key trends in offer characteristics and evaluates how these features relate to transfer behaviour across the Victorian electricity market.

### Discount structure over time

```{r discount-structure}

discount_trends <- offer_snapshots %>%
  filter(n_offers > 0) %>%
  group_by(date) %>%
  summarise(
    avg_guaranteed = round(mean(pct_guaranteed, na.rm = TRUE),2),
    avg_conditional = round(mean(pct_conditional, na.rm = TRUE)),
    avg_no_discount = round(mean(pct_no_discount, na.rm = TRUE)),
    .groups = "drop"
  )

plot_ly(discount_trends) %>%
  add_trace(x = ~date, y = ~avg_guaranteed, type = "scatter", mode = "lines",
            name = "Guaranteed", line = list(color = "#236192", width = 2),
            stackgroup = "one", fillcolor = "#A7C0D3") %>%
  add_trace(x = ~date, y = ~avg_conditional, type = "scatter", mode = "lines",
            name = "Conditional", line = list(color = "#ed8b00", width = 2),
            stackgroup = "one", fillcolor = "#F8D199") %>%
  add_trace(x = ~date, y = ~avg_no_discount, type = "scatter", mode = "lines",
            name = "No Discount", line = list(color = "#75787b", width = 2),
            stackgroup = "one", fillcolor = "#C8C9CA") %>%
  layout(
    title = "<b>Discount Structure Over Time</b>",
    xaxis = list(title = ""),
    yaxis = list(title = "% of Offers"),
    hovermode = "x unified"
  )
```

* 'No discount' offers dominate at ~ 70 - 80% throughout.
* Guaranteed discounts relatively stable at 12-17% of offers in 2025.
* Conditional discounts declining slightly over time.

### Solar and incentive availability over time

```{r feature-availability}

feature_trends <- offer_snapshots %>%
  filter(n_offers > 0) %>%
  group_by(date) %>%
  summarise(
    avg_solar = round(mean(pct_solar, na.rm = TRUE),2),
    avg_incentive = round(mean(pct_incentive, na.rm = TRUE)),
    .groups = "drop"
  )

plot_ly(feature_trends) %>%
  add_trace(x = ~date, y = ~avg_solar, type = "scatter", mode = "lines",
            name = "Solar Available", line = list(color = "#C8C9CA", width = 2)) %>%
  add_trace(x = ~date, y = ~avg_incentive, type = "scatter", mode = "lines",
            name = "With Incentive", line = list(color = "#236192", width = 2)) %>%
  layout(
    title = "<b>Solar & Incentive Availability Over Time</b>",
    xaxis = list(title = ""),
    yaxis = list(title = "% of Offers"),
    hovermode = "x unified"
  )
```

* Near-universal solar availability (96%+) reflects Victoria's high solar penetration
* Decline in incentive offers between 2023-2025 (may signal reduced competitive pressure or better / alternative acquisition strategies).

### Correlation Analysis - Transfers Out Rate

This matrix summarises linear correlations between offer characteristics and the weekly transfer OUT rate.

```{r correlation-matrix}
# Overall correlation matrix
cor_vars_out <- data_out %>%
  select(
    price_vs_market, price_rank, pct_guaranteed, pct_conditional,
    pct_incentive, pct_solar, avg_annual_fee,
    avg_late_fee, rate_out, customer_count
  ) %>%
  mutate(log_customer_count = log(customer_count + 1)) %>%
  select(-customer_count)

cor_matrix_out <- cor(cor_vars_out, use = "pairwise.complete.obs")

corrplot(
  cor_matrix_out,
  method = "color",
  col = colorRampPalette(c("#183028", "white", "#c44536"))(200),
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  number.cex = 0.6,
  title = "Correlation Matrix: Offer Features & Transfer OUT Rate",
  mar = c(0, 0, 2, 0)
)
```

* No strong correlations between transfer rate out and any offer factors.

### Correlation Analysis - Transfers In Rate

This matrix summarises correlations between offer features and the weekly transfer IN rate.

```{r correlation-in}
# Correlation for Transfer IN
cor_vars_in <- data_in %>%
  select(
    price_vs_market, price_rank, pct_guaranteed, pct_conditional,
    pct_incentive, pct_solar, avg_annual_fee,
    avg_late_fee, rate_in, customer_count
  ) %>%
  mutate(log_customer_count = log(customer_count + 1)) %>%
  select(-customer_count)

cor_matrix_in <- cor(cor_vars_in, use = "pairwise.complete.obs")

corrplot(
  cor_matrix_in,
  method = "color",
  col = colorRampPalette(c("#183028", "white", "#c44536"))(200),
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  number.cex = 0.6,
  title = "Correlation Matrix: Offer Features & Transfer IN Rate",
  mar = c(0, 0, 2, 0)
)
```

* No strong correlations between transfer rate in and any offer factors.

### Transfer OUT: Price vs Transfer Rate (All Retailers)

```{r relationship-out-all}
# --- Create ALL plot ---
p_all_out <- ggplotly(
  ggplot(
    data_out %>%
      filter(!is.na(price_vs_market), !is.na(rate_out)),
    aes(x = price_vs_market, y = rate_out)
  ) +
    geom_point(alpha = 0.15, color = "#236192") +
    geom_smooth(method = "loess", color = "#d7191c", linewidth = 1.2) +
    labs(
      title = "Transfer OUT Rate vs Price Position - All Retailers",
      x = "Price vs Market (%)",
      y = "Transfer OUT Rate (%)"
    ) +
    theme_minimal() +
    theme(plot.title = element_text(face = "bold"))
)

p_all_out
```

### Transfer IN: Price vs Transfer Rate (All Retailers)

```{r relationship-in-all}
# Price vs transfers IN
p_all_in <- ggplotly(
  ggplot(data_in %>% filter(!is.na(price_vs_market), !is.na(rate_in)), 
       aes(x = price_vs_market, y = rate_in)) +
  geom_point(alpha = 0.15, color = "#1a9641") +
  geom_smooth(method = "loess", color = "#4986a0", linewidth = 1.2, se = TRUE) +
  labs(
    title = "Transfer IN Rate vs Price Position - All Retailers",
    x = "Price vs Market (%)",
    y = "Transfer IN Rate (%)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))
)

p_all_in
```

## Retailer Size Analysis & Individual Retailer Patterns

This section explores how price competitiveness influences transfers across retailer size categories and examines individual retailer behaviour.

### Transfer OUT vs Price Position — By Retailer Size

```{r key-relationships-large}
# Price vs transfers OUT
p_large_out <- ggplot(data_out %>% 
         filter(
           cprg_retailer_size == "large",
           !is.na(price_vs_market), 
           !is.na(rate_out)), 
       aes(x = price_vs_market, y = rate_out)) +
  geom_point(alpha = 0.15, color = "#236192") +
  geom_smooth(method = "loess", color = "#d7191c", linewidth = 1.2, se = TRUE) +
  labs(
    title = "Transfer OUT Rate vs Price Position - Large Retailers",
    x = "Price vs Market (%)",
    y = "Transfer OUT Rate (%)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))

ggplotly(p_large_out)
```

* Price has a minimal impact on customer retention for large retailers.
* Large retailers tend to have offers that are around the market median (seen by the dense cluster around Price vs Market (%) = 0).
* Cheaper offers have similar transfer-out rates to expensive offers, suggesting customers leave for reasons other than price.
* Transfer out rates are observed to be the highest when large retailer's offers are ~130% higher than market median.

```{r key-relationships-medium}
# Price vs transfers OUT
p_medium_out <- ggplot(data_out %>% 
         filter(
           cprg_retailer_size == "medium",
           !is.na(price_vs_market), 
           !is.na(rate_out)), 
       aes(x = price_vs_market, y = rate_out)) +
  geom_point(alpha = 0.15, color = "#236192") +
  geom_smooth(method = "loess", color = "#d7191c", linewidth = 1.2, se = TRUE) +
  labs(
    title = "Transfer OUT Rate vs Price Position - Medium Retailers",
    x = "Price vs Market (%)",
    y = "Transfer OUT Rate (%)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))

ggplotly(p_medium_out)
```

* Similar to patterns seen for large retailers, however a lot more offers are observed between 200-300% higher than market median.

```{r key-relationships-small}
# Price vs transfers OUT

p_small_out <- ggplot(data_out %>% 
         filter(
           cprg_retailer_size == "small",
           !is.na(price_vs_market), 
           !is.na(rate_out)), 
       aes(x = price_vs_market, y = rate_out)) +
  geom_point(alpha = 0.15, color = "#236192") +
  geom_smooth(method = "loess", color = "#d7191c", linewidth = 1.2, se = TRUE) +
  labs(
    title = "Transfer OUT Rate vs Price Position - Small Retailers",
    x = "Price vs Market (%)",
    y = "Transfer OUT Rate (%)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))

ggplotly(p_small_out)
```

* Small retailer customer are slightly more responsive to higher prices howevere the relationhsip is still very weak.

### Transfer In vs Price Position — By Retailer Size

```{r relationship-in - large}

p_large_in <- ggplot(data_in %>% filter(!is.na(price_vs_market), !is.na(rate_in),
                          cprg_retailer_size == "large"), 
       aes(x = price_vs_market, y = rate_in)) +
  geom_point(alpha = 0.15, color = "#1a9641") +
  geom_smooth(method = "loess", color = "#4986a0", linewidth = 1.2, se = TRUE) +
  labs(
    title = "Transfer IN Rate vs Price Position - Large Retailers",
    x = "Price vs Market (%)",
    y = "Transfer IN Rate (%)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))

ggplotly(p_large_in)
```

```{r relationship-in - medium}

p_medium_in <- ggplot(data_in %>% filter(!is.na(price_vs_market), !is.na(rate_in),
                          cprg_retailer_size == "medium"), 
       aes(x = price_vs_market, y = rate_in)) +
  geom_point(alpha = 0.15, color = "#1a9641") +
  geom_smooth(method = "loess", color = "#4986a0", linewidth = 1.2, se = TRUE) +
  labs(
    title = "Transfer IN Rate vs Price Position - Medium Retailers",
    x = "Price vs Market (%)",
    y = "Transfer IN Rate (%)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))


ggplotly(p_medium_in)
```

```{r relationship-in - small}

p_small_in <- ggplot(data_in %>% filter(!is.na(price_vs_market), !is.na(rate_in),
                          cprg_retailer_size == "small"), 
       aes(x = price_vs_market, y = rate_in)) +
  geom_point(alpha = 0.15, color = "#1a9641") +
  geom_smooth(method = "loess", color = "#4986a0", linewidth = 1.2, se = TRUE) +
  labs(
    title = "Transfer IN Rate vs Price Position - Small Retailers",
    x = "Price vs Market (%)",
    y = "Transfer IN Rate (%)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))

ggplotly(p_small_in)
```

### Individual Retailer Patterns (Faceted Plots)

Shows if patterns differ by retailer.

<b>4.3.1 Transfer Out - Faceted by Retailer</b>

```{r retailer-patterns}

ggplot(data_out %>% filter(!is.na(price_vs_market)), 
       aes(x = price_vs_market, y = rate_out)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", se = FALSE, color = "#4986a0") +
  facet_wrap(~retailer, scales = "free_y") +
  labs(title = "Price-Transfer OUT Relationship by Retailer",
       x = "Price vs Market (%)", y = "Transfer OUT Rate (%)") +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))
```

<b>4.3.2 Transfer In - Faceted by Retailer</b>

```{r retailer-patterns-in}
# Retailer patterns for Transfer IN
ggplot(data_in %>% filter(!is.na(price_vs_market)), 
       aes(x = price_vs_market, y = rate_in)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", se = FALSE, color = "#1a9641") +
  facet_wrap(~retailer, scales = "free_y") +
  labs(title = "Price-Transfer IN Relationship by Retailer",
       x = "Price vs Market (%)", y = "Transfer IN Rate (%)") +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))
```

* There is a huge diversity in price-transfer patterns across the different retailers.
* Some retailers have highly price-sensitive customers while others show no relationship (horizontal line).
* Indicates differentiated value proposisions beyond price.

### Retailer-Specific Correlation Heatmaps

<b>4.4.1 Transfer Out - Correlation Heatmap</b>

```{r retailer-correlation-heatmaps-out, fig.width=18, fig.height=22}
# Correlation heatmaps by retailer
vars_for_cor <- c(
  "price_vs_market", "pct_guaranteed", "pct_conditional",
  "pct_incentive", "pct_solar",
  "avg_annual_fee", "avg_late_fee", "rate_out"
)

predictor_vars <- setdiff(vars_for_cor, "rate_out")

retailers_with_data <- data_out %>%
  group_by(retailer) %>%
  summarise(
    any_non_missing = any(!is.na(across(all_of(predictor_vars))))
  ) %>%
  filter(any_non_missing) %>%
  pull(retailer)

data_out <- data_out %>%
  filter(retailer %in% retailers_with_data)

cor_by_retailer <- data_out %>%
  select(retailer, all_of(vars_for_cor)) %>%
  group_by(retailer) %>%
  do({
    cor_mat <- cor(.[vars_for_cor], use = "pairwise.complete.obs")
    cor_df <- as.data.frame(as.table(cor_mat))
    names(cor_df) <- c("Var1", "Var2", "Correlation")
    cor_df
  }) %>%
  ungroup()

ggplot(cor_by_retailer, aes(Var1, Var2, fill = Correlation)) +
  geom_tile() +
  scale_fill_gradient2(
    low = "#183028", mid = "white", high = "#c44536",
    midpoint = 0, limits = c(-1, 1)
  ) +
  facet_wrap(~ retailer, ncol = 3) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    strip.text = element_text(size = 14, face = "bold"),
    plot.title = element_text(face = "bold", size = 16)
  ) +
  labs(
    title = "Correlation Heatmaps by Retailer (Transfer OUT)",
    x = "", y = ""
  )
```

<b>4.4.2 Transfer In - Correlation Heatmap</b>

```{r retailer-correlation-heatmaps-in, fig.width=18, fig.height=22}
# Correlation heatmaps by retailer (Transfer IN)
vars_for_cor_in <- c(
  "price_vs_market", "pct_guaranteed", "pct_conditional",
  "pct_incentive", "pct_solar",
  "avg_annual_fee", "avg_late_fee", "rate_in"
)

predictor_vars_in <- setdiff(vars_for_cor_in, "rate_in")

# Filter retailers with any non-missing predictor data
retailers_with_data_in <- data_in %>%
  group_by(retailer) %>%
  summarise(
    any_non_missing = any(!is.na(across(all_of(predictor_vars_in))))
  ) %>%
  filter(any_non_missing) %>%
  pull(retailer)

data_in_filtered <- data_in %>%
  filter(retailer %in% retailers_with_data_in)

cor_by_retailer_in <- data_in_filtered %>%
  select(retailer, all_of(vars_for_cor_in)) %>%
  group_by(retailer) %>%
  do({
    cor_mat <- cor(.[vars_for_cor_in], use = "pairwise.complete.obs")
    cor_df <- as.data.frame(as.table(cor_mat))
    names(cor_df) <- c("Var1", "Var2", "Correlation")
    cor_df
  }) %>%
  ungroup()

ggplot(cor_by_retailer_in, aes(Var1, Var2, fill = Correlation)) +
  geom_tile() +
  scale_fill_gradient2(
    low = "#183028", mid = "white", high = "#c44536",
    midpoint = 0, limits = c(-1, 1)
  ) +
  facet_wrap(~ retailer, ncol = 3) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    strip.text = element_text(size = 14, face = "bold"),
    plot.title = element_text(face = "bold", size = 16)
  ) +
  labs(
    title = "Correlation Heatmaps by Retailer (Transfer IN)",
    x = "", y = ""
  )
```

## Price Position Analysis (With Lag Periods)

### Segmented Lag Analysis — Transfers Out

Examines how retailer price position (relative to the Victorian market median) affects weekly transfer OUT rates, including lagged effects up to eight weeks.

```{r price-segmentation-out}
segment_analysis <- function(data, price_col, rate_col, lag_name) {
  data %>%
    filter(!is.na(.data[[price_col]]), !is.na(.data[[rate_col]])) %>%
    mutate(price_group = case_when(
      .data[[price_col]] > 10 ~ "Much higher (>10%)",
      .data[[price_col]] > 5 ~ "Higher (5-10%)",
      .data[[price_col]] > -5 ~ "Average (±5%)",
      .data[[price_col]] > -10 ~ "Lower (5-10%)",
      TRUE ~ "Much lower (<-10%)"
    ) %>% factor(levels = c("Much lower (<-10%)", "Lower (5-10%)", "Average (±5%)",
                             "Higher (5-10%)", "Much higher (>10%)"))) %>%
    group_by(price_group) %>%
    summarise(
      avg_rate = mean(.data[[rate_col]], na.rm = TRUE),
      median_rate = median(.data[[rate_col]], na.rm = TRUE),
      n = n(),
      .groups = "drop"
    ) %>%
    mutate(lag = lag_name)
}

seg_out <- bind_rows(
  segment_analysis(data_out, "price_vs_market", "rate_out", "Current Week"),
  segment_analysis(data_out, "price_vs_market_lag2w", "rate_out", "2 Weeks Ago"),
  segment_analysis(data_out, "price_vs_market_lag4w", "rate_out", "4 Weeks Ago"),
  segment_analysis(data_out, "price_vs_market_lag8w", "rate_out", "8 Weeks Ago")
) %>%
  mutate(lag = factor(lag, levels = c("Current Week", "2 Weeks Ago",
                                       "4 Weeks Ago", "8 Weeks Ago")))

plot_ly(seg_out, x = ~price_group, y = ~avg_rate, color = ~lag, type = "bar",
        colors = c("#236192", "#4986a0", "#75787b", "#d0d0d0"),
        text = ~paste0(round(avg_rate, 3), "%"), textposition = "outside") %>%
  layout(
    margin = list(t=120),
    title = "<b>Transfer OUT Rate by Price Position (All Lag Periods)</b>",
    xaxis = list(title = "Price vs Market"),
    yaxis = list(title = "Average Transfer Out Rate (%)"),
    barmode = "group",
    legend = list(orientation = "h", y = 1.15, x = 0.5, xanchor = "center")
  )
```

````{r difference-from-baseline-out}
# Difference from average chart - Transfer OUT
segmented_differences_out <- seg_out %>%
  group_by(lag) %>%
  mutate(
    avg_baseline = avg_rate[price_group == "Average (±5%)"],
    difference_from_baseline = avg_rate - avg_baseline,
    pct_difference = (difference_from_baseline / avg_baseline) * 100
  ) %>%
  ungroup()

plot_ly(
  data = segmented_differences_out,
  x = ~price_group,
  y = ~difference_from_baseline,
  color = ~lag,
  type = "bar",
  colors = c("#236192", "#4986a0", "#75787b", "#a8a8a8", "#d0d0d0")
) %>%
  layout(
    title = "<b>Difference in Transfer OUT Rates vs Average Price Group</b>",
    xaxis = list(title = "Price vs Market"),
    yaxis = list(title = "Difference from Baseline (percentage points)"),
    margin = list(t = 110),
    barmode = "group",
    legend = list(
      orientation = "h", 
      y = 1.15, 
      x = 0.5, 
      xanchor = "center",
      font = list(size = 10)
    ),
    shapes = list(
      list(
        type = "line",
        x0 = -0.5, x1 = 5,
        y0 = 0, y1 = 0,
        line = list(color = "gray", dash = "dash", width = 2)
      )
    )
  )
````

### Segmented Lag Analysis — Transfers In

```{r}
seg_in <- bind_rows(
  segment_analysis(data_in, "price_vs_market", "rate_in", "Current Week"),
  segment_analysis(data_in, "price_vs_market_lag1w", "rate_in", "1 Week Ago"),
  segment_analysis(data_in, "price_vs_market_lag2w", "rate_in", "2 Weeks Ago"),
  segment_analysis(data_in, "price_vs_market_lag4w", "rate_in", "4 Weeks Ago"),
  segment_analysis(data_in, "price_vs_market_lag8w", "rate_in", "8 Weeks Ago")
  ) %>%
  mutate(lag = factor(lag, levels = c("Current Week", "1 Week Ago", 
                                      "2 Weeks Ago", "4 Weeks Ago", "8 Weeks Ago")))

plot_ly(
  seg_in, x = ~price_group, y = ~avg_rate, color = ~lag, type = "bar",
  colors = c("#1a9641", "#66c2a5", "#abdda4", "#d9f0d3", "#f7fcf5"),
  text = ~sprintf("%.2f%%", avg_rate), textposition = "outside") %>%
  layout(
    title = "<b>Transfer IN Rate by Price Position (Lag Comparison)</b>",
    xaxis = list(title = "Retailer Price vs Market Position"),
    yaxis = list(title = "Average Transfer IN Rate (%)"),
    barmode = "group",
    legend = list(orientation = "h", y = 1.15, x = 0.5, xanchor = "center")
  )
```

```{r}
segmented_differences_in <- seg_in %>%
  group_by(lag) %>%
  mutate(
    baseline = avg_rate[price_group == "Average (±5%)"],
    difference_pp = avg_rate - baseline,
    difference_pct = (difference_pp / baseline) * 100) %>%
  ungroup()

plot_ly(
  segmented_differences_in, x = ~price_group, y = ~difference_pp, color = ~lag,
  type = "bar",
  colors = c("#1a9641", "#66c2a5", "#abdda4", "#d9f0d3", "#f7fcf5")) %>%
  layout(
    title = "<b>Deviation from Average Transfer IN Rate (±5% price group)</b>",
    xaxis = list(title = "Price Group"),
    yaxis = list(title = "Difference (percentage points)"),
    barmode = "group",
    margin = list(t = 110),
    shapes = list(
    list(
    type = "line",
    x0 = -0.5, x1 = 5,
    y0 = 0, y1 = 0,
    line = list(color = "gray", dash = "dash", width = 2)))
  )
```

## Transfer Out Modelling

This section evaluates how offer characteristics explain weekly transfer OUT rates using linear models, polynomial models, interaction models, and machine-learning methods.

### Prepare Dataset for Modelling

```{r prepare-regression-out}
reg_data_out <- data_out %>%
  filter(
    !is.na(price_vs_market),
    !is.na(pct_solar), !is.na(pct_incentive),
    !is.na(pct_guaranteed), !is.na(avg_annual_fee),
    !is.na(avg_late_fee), !is.na(customer_count)
  ) %>%
  mutate(
    total_out = as.numeric(total_out),
    log_customers = log(customer_count + 1)
  )
```

### Model 1: Linear Regression

```{r linear-model-out, results='markup', comment=''}

model_linear_out <- lm(
  rate_out ~ price_vs_market + price_rank + pct_guaranteed + pct_conditional +
    pct_solar + pct_incentive + avg_annual_fee +
    avg_late_fee + log_customers,
  data = reg_data_out
)

linear_r2_out <- summary(model_linear_out)$r.squared
linear_adj_r2_out <- summary(model_linear_out)$adj.r.squared

# Extract coefficients
coef_linear_out <- broom::tidy(model_linear_out) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    significant = p.value < 0.05,
    sig_level = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      TRUE ~ ""
    )
  ) %>%
  arrange(p.value)

print(summary(model_linear_out))
```

### Model 2: Polynomial Regression

```{r polynomial-model-out, results='markup', comment=''}
model_poly_out <- lm(
  rate_out ~ price_vs_market + I(price_vs_market^2) +
    pct_guaranteed + I(pct_guaranteed^2) +
    pct_conditional + I(pct_conditional^2) +
    pct_incentive + I(pct_incentive^2) +
    avg_annual_fee + I(avg_annual_fee^2) +
    avg_late_fee + log_customers,
  data = reg_data_out
)

poly_r2_out <- summary(model_poly_out)$r.squared
poly_adj_r2_out <- summary(model_poly_out)$adj.r.squared

print(summary(model_poly_out))
```

### Model 3: Interaction Effects

```{r interaction-model-out, results='markup', comment=''}
model_interact_out <- lm(
  rate_out ~ price_vs_market * pct_conditional +
    price_vs_market * avg_annual_fee +
    pct_guaranteed * pct_incentive +
    log_customers * price_vs_market +
    price_rank + pct_solar + avg_annual_fee + avg_late_fee,
  data = reg_data_out
)

interact_r2_out <- summary(model_interact_out)$r.squared
interact_adj_r2_out <- summary(model_interact_out)$adj.r.squared

# Show significant interactions
interact_coef_out <- broom::tidy(model_interact_out) %>%
  filter(grepl(":", term), p.value < 0.05) %>%
  arrange(p.value)

print(summary(model_interact_out))
```

### Model 4: Random Forest

```{r random-forest-outE, results='markup', comment=''}
rf_data_out <- reg_data_out %>%
  select(rate_out, price_vs_market, price_rank, pct_guaranteed, pct_conditional,
         pct_solar, pct_incentive, avg_annual_fee,
         avg_late_fee, log_customers) %>%
  na.omit()

set.seed(123)
rf_out <- randomForest(
  rate_out ~ .,
  data = rf_data_out,
  ntree = 500,
  importance = TRUE,
  mtry = 3
)

# Calculate R²
rf_predictions <- predict(rf_out, rf_data_out)
rf_ss_res <- sum((rf_data_out$rate_out - rf_predictions)^2)
rf_ss_tot <- sum((rf_data_out$rate_out - mean(rf_data_out$rate_out))^2)
rf_r2_out <- 1 - (rf_ss_res / rf_ss_tot)

importance_out <- importance(rf_out) %>%
as.data.frame() %>%
tibble::rownames_to_column("Variable") %>%
arrange(desc(`%IncMSE`))

print(rf_out)
```

```{r}
# Plot importance
plot_ly(head(importance_out, 10),
        x = ~reorder(Variable, `%IncMSE`), y = ~`%IncMSE`,
        type = "bar", marker = list(color = "#236192"),
        text = ~round(`%IncMSE`, 1), textposition = "outside") %>%
  layout(
    title = "<b>Random Forest: Variable Importance (Transfer OUT)</b>",
    xaxis = list(title = "", tickangle = -45),
    yaxis = list(title = "% Increase in MSE")
  )
```

### Model 5: XGBoost

```{r xgboost-out, results='markup', comment=''}
xgb_features_out <- rf_data_out %>% select(-rate_out) %>% as.matrix()
xgb_label_out <- rf_data_out$rate_out
xgb_data_out <- xgb.DMatrix(data = xgb_features_out, label = xgb_label_out)

set.seed(123)
xgb_out <- xgboost(
  data = xgb_data_out,
  nrounds = 100,
  max_depth = 6,
  eta = 0.1,
  objective = "reg:squarederror",
  verbose = 0
)

# Calculate R²
xgb_predictions <- predict(xgb_out, xgb_features_out)
xgb_ss_res <- sum((xgb_label_out - xgb_predictions)^2)
xgb_ss_tot <- sum((xgb_label_out - mean(xgb_label_out))^2)
xgb_r2_out <- 1 - (xgb_ss_res / xgb_ss_tot)

# Feature importance
xgb_importance_out <- xgb.importance(
  feature_names = colnames(xgb_features_out),
  model = xgb_out
)

print(xgb_out)
```

```{r}
# Plot importance
plot_ly(xgb_importance_out,
        x = ~reorder(Feature, Gain), y = ~Gain,
        type = "bar", marker = list(color = "#c44536"),
        text = ~round(Gain, 4), textposition = "outside") %>%
  layout(
    title = "<b>XGBoost: Feature Importance (Transfer OUT)</b>",
    xaxis = list(title = "", tickangle = -45),
    yaxis = list(title = "Gain")
  )
```

### Model Comparison

```{r model-comparison-out}
model_comparison_out <- data.frame(
  Model = c("Linear Regression", "Polynomial Regression", "Interaction Model",
            "Random Forest", "XGBoost"),
  R_Squared = c(linear_r2_out, poly_r2_out, interact_r2_out, rf_r2_out, xgb_r2_out),
  Adj_R_Squared = c(linear_adj_r2_out, poly_adj_r2_out, interact_adj_r2_out, NA, NA)
) %>%
  arrange(desc(R_Squared))

kable(
  model_comparison_out,
  "html",
  caption = "Model Comparison – Transfer OUT"
  ) %>%
kable_styling(full_width = FALSE, position = "left")
```

## Transfer In Modelling

### Prepare Dataset for Modelling

```{r prepare-regression-in}
reg_data_in <- data_in %>%
  filter(
    !is.na(price_vs_market),
    !is.na(pct_solar), !is.na(pct_incentive),
    !is.na(pct_guaranteed), !is.na(avg_annual_fee),
    !is.na(avg_late_fee), !is.na(customer_count)
  ) %>%
  mutate(
    total_in = as.numeric(total_in),
    log_customers = log(customer_count + 1)
  )
```

### Model 1: Linear Regression

```{r linear-model-in, results='markup', comment=''}
model_linear_in <- lm(
  rate_in ~ price_vs_market + price_rank + pct_guaranteed + pct_conditional +
    pct_solar + pct_incentive + avg_annual_fee +
    avg_late_fee + log_customers,
  data = reg_data_in
)

linear_r2_in <- summary(model_linear_in)$r.squared
linear_adj_r2_in <- summary(model_linear_in)$adj.r.squared

coef_linear_in <- broom::tidy(model_linear_in) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    significant = p.value < 0.05,
    sig_level = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      TRUE ~ ""
    )
  ) %>%
  arrange(p.value)

print(summary(model_linear_in))
```

### Model 2: Polynomial Regression

```{r polynomial-model-in, results='markup', comment=''}
model_poly_in <- lm(
  rate_in ~ price_vs_market + I(price_vs_market^2) +
    pct_guaranteed + I(pct_guaranteed^2) +
    pct_conditional + I(pct_conditional^2) +
    pct_incentive + I(pct_incentive^2) +
    avg_annual_fee + I(avg_annual_fee^2) +
    avg_late_fee + log_customers,
  data = reg_data_in
)

poly_r2_in <- summary(model_poly_in)$r.squared
poly_adj_r2_in <- summary(model_poly_in)$adj.r.squared

print(summary(model_poly_in))
```

### Model 3: Interaction Effects

```{r interaction-model-in, results='markup', comment=''}
model_interact_in <- lm(
  rate_in ~ price_vs_market * pct_conditional +
    price_vs_market * avg_annual_fee +
    pct_guaranteed * pct_incentive +
    log_customers * price_vs_market +
    price_rank + pct_solar + avg_annual_fee + avg_late_fee,
  data = reg_data_in
)


interact_r2_in <- summary(model_interact_in)$r.squared
interact_adj_r2_in <- summary(model_interact_in)$adj.r.squared

# Show significant interactions
interact_coef_in <- broom::tidy(model_interact_in) %>%
  filter(grepl(":", term), p.value < 0.05) %>%
  arrange(p.value)

print(summary(model_interact_in))
```

### Model 4: Random Forest

```{r random-forest-in, results='markup', comment=''}
rf_data_in <- reg_data_in %>%
  select(rate_in, price_vs_market, price_rank, pct_guaranteed, pct_conditional,
         pct_solar, pct_incentive, avg_annual_fee,
         avg_late_fee, log_customers) %>%
  na.omit()

set.seed(123)
rf_in <- randomForest(
  rate_in ~ .,
  data = rf_data_in,
  ntree = 500,
  importance = TRUE,
  mtry = 3
)

# Calculate R²
rf_predictions_in <- predict(rf_in, rf_data_in)
rf_ss_res_in <- sum((rf_data_in$rate_in - rf_predictions_in)^2)
rf_ss_tot_in <- sum((rf_data_in$rate_in - mean(rf_data_in$rate_in))^2)
rf_r2_in <- 1 - (rf_ss_res_in / rf_ss_tot_in)

# Variable importance
importance_in <- importance(rf_in) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Variable") %>%
  arrange(desc(`%IncMSE`))

print(rf_in)
```

```{r}
# Plot importance
plot_ly(head(importance_in, 10),
        x = ~reorder(Variable, `%IncMSE`), y = ~`%IncMSE`,
        type = "bar", marker = list(color = "#1a9641"),
        text = ~round(`%IncMSE`, 1), textposition = "outside") %>%
  layout(
    title = "<b>Random Forest: Variable Importance (Transfer IN)</b>",
    xaxis = list(title = "", tickangle = -45),
    yaxis = list(title = "% Increase in MSE")
  )
```

### Model 5: XGBoost

```{r xgboost-in, results='markup', comment=''}
xgb_features_in <- rf_data_in %>% select(-rate_in) %>% as.matrix()
xgb_label_in <- rf_data_in$rate_in
xgb_data_in <- xgb.DMatrix(data = xgb_features_in, label = xgb_label_in)

set.seed(123)
xgb_in <- xgboost(
  data = xgb_data_in,
  nrounds = 100,
  max_depth = 6,
  eta = 0.1,
  objective = "reg:squarederror",
  verbose = 0
)

# Calculate R²
xgb_predictions_in <- predict(xgb_in, xgb_features_in)
xgb_ss_res_in <- sum((xgb_label_in - xgb_predictions_in)^2)
xgb_ss_tot_in <- sum((xgb_label_in - mean(xgb_label_in))^2)
xgb_r2_in <- 1 - (xgb_ss_res_in / xgb_ss_tot_in)

# Feature importance
xgb_importance_in <- xgb.importance(
  feature_names = colnames(xgb_features_in),
  model = xgb_in
)

print(xgb_in)
```

```{r}
# Plot importance
plot_ly(xgb_importance_in,
        x = ~reorder(Feature, Gain), y = ~Gain,
        type = "bar", marker = list(color = "#4986a0"),
        text = ~round(Gain, 4), textposition = "outside") %>%
  layout(
    title = "<b>XGBoost: Feature Importance (Transfer IN)</b>",
    xaxis = list(title = "", tickangle = -45),
    yaxis = list(title = "Gain")
  )
```

### Model Comparison (Transfer IN)

```{r model-comparison-in}
model_comparison_in <- data.frame(
  Model = c("Linear Regression", "Polynomial Regression", "Interaction Model",
            "Random Forest", "XGBoost"),
  R_Squared = c(linear_r2_in, poly_r2_in, interact_r2_in, rf_r2_in, xgb_r2_in),
  Adj_R_Squared = c(linear_adj_r2_in, poly_adj_r2_in, interact_adj_r2_in, NA, NA)
) %>%
  arrange(desc(R_Squared))
```

```{r}
kable(
  model_comparison_in,
  "html",
  caption = "Model Comparison – Transfer IN"
  ) %>%
kable_styling(full_width = FALSE, position = "left")
```

## Comparison: OUT vs IN Drivers

This section directly compares the linear regression coefficients from the OUT and IN models, highlighting whether predictors:

### Coefficient Comparison Table

```{r coefficient-comparison}
# Combine OUT and IN coefficients
coef_comparison <- coef_linear_out %>%
  select(term, estimate_out = estimate, p_out = p.value, sig_out = significant) %>%
  full_join(
    coef_linear_in %>%
      select(term, estimate_in = estimate, p_in = p.value, sig_in = significant),
    by = "term"
  ) %>%
  mutate(
    sig_out = replace_na(sig_out, FALSE),
    sig_in = replace_na(sig_in, FALSE),
    interpretation = case_when(
      sig_out & sig_in & sign(estimate_out) == sign(estimate_in) ~ "Same direction (both)",
      sig_out & sig_in & sign(estimate_out) != sign(estimate_in) ~ "Opposite effects ⚠️",
      sig_out & !sig_in ~ "Only affects OUT",
      !sig_out & sig_in ~ "Only affects IN",
      TRUE ~ "Not significant"
    ),
    direction_out = case_when(
      !sig_out ~ "",
      estimate_out > 0 ~ "↑ Increases OUT",
      TRUE ~ "↓ Decreases OUT"
    ),
    direction_in = case_when(
      !sig_in ~ "",
      estimate_in > 0 ~ "↑ Increases IN",
      TRUE ~ "↓ Decreases IN"
    )
  )
```

```{r}
kable(
  coef_comparison %>%
  select(
  Predictor = term,
  Estimate_OUT = estimate_out,
  Estimate_IN = estimate_in,
  Interpretation = interpretation
  ) %>%
  arrange(desc(abs(Estimate_OUT))),
  "html",
  caption = "Comparison of Predictors Affecting OUT vs IN Transfers"
  ) %>%
kable_styling(full_width = FALSE, position = "left") %>%
kable_paper(lightable_options = "striped")
```

